(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-09 ms.tex
blah

Table \ref{table:FPP} summarizes the results of these
calculations, presenting the relative probability for each candidate
to be caused by any of three false positive scenarios: an undiluted
eclipsing binary (EB), a hierarchical triple eclipsing binary (HEB),
and a chance-aligned background(/foreground) eclipsing binary (BEB).

@@

>>>>

Table \ref{Tab:FPP} summarizes the results of these
calculations, presenting the relative probability for each candidate
to be caused by any of three false positive scenarios: an undiluted
eclipsing binary (EB), a hierarchical triple eclipsing binary (HEB),
and a chance-aligned background(/foreground) eclipsing binary (BEB).

@@

%\include{table_fpp}
